### 2015-02-27 icfp15-servo/rust.tex
Rudimentary Rust overview

TODO: basic overview, covering systems language basis; borrowing/ownership \& region/MLKit connection; ADT \& pattern matching; traits \& generics

\subsection{Concurrency and parallelism}

Rust contains library functionality for concurrency and data parallelism.
Concurrency, in particular, integrates cleanly with Rust's ownership types.
In safe concurrent programs, the data operated on by distinct threads is also itself distinct.
Through the use of Rust's ownership model, data cannot be owned by two threads at the same time.
For example, the following code generates a static error from the compiler because after the first
thread is spawned, the ownership of \lstinline{data} has been transferred into the closure associated
with that thread and is unavailable for transfer in to the closure for the second thread.
%http://is.gd/tkcD9R
\begin{lstlisting}
fn main() {
  let mut data = Box::new(0);

>>>>

Rust is a statically typed systems programming language most heavily inspired by the C
and ML families of languages~\cite{RUST}.
Like the C family of languages, it provides the developer control over the use of system
resources and facilities along with predictable performance.
In addition, it provides an ownership-based type system inspired by the region systems work in the
MLKit project~\cite{mlkit} and especially as implemented in the Cyclone project~\cite{cyclone}.
Unlike the ownership system in the Singularity project~\cite{singularity}, Rust allows APIs to
not only transfer ownership but also to temporarily \emph{borrow} values, significantly
reducing the number of region and ownership annotations required in large programs.
Rust also builds on ideas from typeclasses and type families in Haskell~\cite{haskell}.
Complete documentation and a language reference for Rust are available at: \url{http://doc.rust-lang.org/}.

\subsection{Concurrency and parallelism}
Rust contains library functionality for concurrency and data parallelism.
Concurrency, in particular, integrates cleanly with Rust's ownership types.
In safe concurrent programs, the data operated on by distinct threads is also itself distinct.
Through the use of Rust's ownership model, data cannot be owned by two threads at the same time.
For example, the following code generates a static error from the compiler because after the first
thread is spawned, the ownership of \lstinline{data} has been transferred into the closure associated
with that thread and is unavailable for transfer in to the closure for the second thread.
%http://is.gd/tkcD9R
\begin{lstlisting}
fn main() {
  let mut data = Box::new(0);
